Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-03-30 r_scripts/parallel_presentation.Rmd
small

@@

clusterExport(cl, "or_zip_map", envir = .GlobalEnv)
clusterExport(cl, "or_zip_name", envir = .GlobalEnv)
clusterExport(cl, "smoke_grid", envir = .GlobalEnv)
clusterExport(cl, "wrf_grid_name", envir = .GlobalEnv)
clusterExport(cl, "zip_wrf_proportion", envir = .GlobalEnv)

@@

```{r forloop, echo = FALSE}
start <- proc.time()
for (i in 201:300) {
  # output value of zipcode
  zipcode <- as.character(or_zip_name[i]) 
  # limit shapefile to particular zipcode
  zip_shape <- or_zip_map[or_zip_map$ZCTA5CE10 %in% zipcode, ]
  # convert to polygon
  zip_poly <-SpatialPolygons(zip_shape@polygons)
for(j in 201:300){
    # output each grid and create a polygon
    wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == j, ]
    # now what about grid 719; should be much less
    wrf_poly <- SpatialPolygons(wrf_grid@polygons)

@@

vars1 <- c(1:1610)
f2 <- function(n){
  wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == n,] # sp df
  # now what about grid 719; should be much less
  wrf_poly <- SpatialPolygons(wrf_grid@polygons) # sp
}
wrf_polygon <- lapply(vars1, f2) # list of 1610 wrf_grid

@@

}
proportion1 <- mapply(f3, rep(201:300, each=100), rep(201:300,100))
stop <- proc.time() - start
stop

@@

}
proportion <- mcmapply(f3, rep(201:300, each=100), rep(201:300,100))
stop <- proc.time() - start
stop

>>>>

vars1 <- c(1:1610)
z <- rep(201:300, each=100)
w <- rep(201:300,100)

@@

clusterExport(cl, "or_zip_map", envir = .GlobalEnv)
clusterExport(cl, "or_zip_name", envir = .GlobalEnv)
clusterExport(cl, "smoke_grid", envir = .GlobalEnv)
clusterExport(cl, "wrf_grid_name", envir = .GlobalEnv)
clusterExport(cl, "zip_wrf_proportion", envir = .GlobalEnv)
clusterExport(cl, "z", envir = .GlobalEnv)
clusterExport(cl, "w", envir = .GlobalEnv)
clusterExport(cl, "vars1", envir = .GlobalEnv)

@@

```{r forloop, echo = FALSE}
start <- proc.time()
for (i in 201:300) {
  # output value of zipcode
  zipcode <- or_zip_name[i]
  # limit shapefile to particular zipcode
  zip_shape <- or_zip_map[or_zip_map$ZCTA5CE10 %in% zipcode, ]
  # convert to polygon
  zip_poly <-SpatialPolygons(zip_shape@polygons)
for(j in 201:300){
    # output each grid and create a polygon
    wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == j, ]
    wrf_poly <- SpatialPolygons(wrf_grid@polygons)

@@

f2 <- function(n){
  wrf_grid <- smoke_grid[smoke_grid@data$WRFGRID_ID == n,] # sp df
  # now what about grid 719; should be much less
  wrf_poly <- SpatialPolygons(wrf_grid@polygons) # sp
}
wrf_polygon <- lapply(vars1, f2) # list of 1610 wrf_grid

@@

}
proportion1 <- mapply(f3, z, w)
stop <- proc.time() - start
stop

@@

}
proportion <- mcmapply(f3, z, w)
stop <- proc.time() - start
stop
